Datasheet for 'Anxiety_or_Depression

### 2024-04-19 outputs/paper/datasheet_template.qmd
Edit datasheet

---
title: "Datasheet for 'Indicators_of_Anxiety_or_Depression_Based_on_Reported_Frequency_of_Symptoms_During_Last_7_Days_20240401'"
author: Chay Park
thanks: "Code and data are available at: https://github.com/Chay-HyunminPark/Anxiety_depressive_disorder"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

@online{cdc_nchs_rate,
    title = {Indicators of Anxiety or Depression Based on Reported Frequency of Symptoms During Last 7 Days},
    author = {National Center for Health Statistics},
    year = {2024},
    url = {https://data.cdc.gov/NCHS/Indicators-of-Anxiety-or-Depression-Based-on-Repor/8pt5-q6wp/about_data},
    organization = {National Center for Health Statistics},
    address = {United States},
    note = {Accessed on April 1, 2024},
}

>>>>

---
title: "Datasheet for 'Anxiety_or_Depression'"
author: Chay Park
thanks: "Code and data are available at: https://github.com/Chay-HyunminPark/Anxiety_depressive_disorder"
date: today
date-format: long
abstract: "The Household Pulse Survey, conducted by the U.S. Census Bureau in collaboration with several federal agencies, serves as a critical dataset to evaluate the socioeconomic and health impacts of the COVID-19 pandemic on American households. This dataset includes self-reported data collected through an internet questionnaire, focusing on areas such as mental health, economic status, and educational disruptions. The survey employs a probabilistic sampling strategy from the Census Bureau's Master Address File to ensure representativeness, with data being weighted according to demographic benchmarks. This datasheet provides detailed insights into the dataset’s composition, collection process, usage, distribution, and maintenance, offering essential information for researchers and policymakers utilizing this resource to understand and respond to the pandemic's effects."
format: pdf
number-sections: true
bibliography: references.bib
---

@@
